### 2023-05-16 application.tex
sections

Since for lossy channel systems $(Q, \Sigma,d,...)$ with $d$ fifo channels and a set $L \subseteq Q \times (\Sigma^*)^d$, the set $\pred^*(\uparrow L)$ is a computable upward-closed regular language, we deduce :

@@

@@

\begin{proof}
Resilience is decidable for lossy counter machines with $\Safe$ and $\Bad$ semilinear sets as a consequence of Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that implies that $\pred^*(\Safe)$ is a computable semilinear set. Hence since the inclusion between two semilinear sets is decidable, we deduce that  $\Bad \subseteq \pred^*(\Safe)$ is decidable.
\end{proof}

@@

\begin{proof}
	\alain{à faire}	Recall that reachability is NP-complete for integer VASS. We consider semilinear sets in $\mathbb{Z}^d$.
\end{proof}

>>>>

Since for lossy channel systems $(Q, \Sigma,d,...)$ with $d$ fifo channels and a set of states $L \subseteq Q \times (\Sigma^*)^d$, the set $\pred^*(\uparrow L)$ is a computable upward-closed regular language, we deduce :

@@

Resilience is also decidable for other class of counter machines for which the reachability relation can be expressed in a decidable logics.

@@

\begin{proof}
We deduce from Theorem 3.6 in \cite{DBLP:conf/rp/Schnoebelen10} that $\pred^*(\Safe)$ is a computable semilinear set if $\Safe$ is semilinear. Hence since the inclusion between two semilinear sets is decidable, we deduce that $\Bad \subseteq \pred^*(\Safe)$ is decidable if $\Bad$ is semilinear.
\end{proof}

@@

\begin{proof}
The reachability relation of integer $d$-VASS is definable by a sentence in Presburger in $\mathbb{Z}^d$ hence	$\Bad \subseteq \pred^*(\Safe)$ is decidable when $\Safe$ and $\Bad$ are semilinear sets. \alain{à faire}	Recall that reachability is NP-complete for integer VASS.
\end{proof}
